Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-13 vesicle_code/docs/permeableVes/main.tex
finished up first draft for relaxation tensions
yny

\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} A contracting geometry
  similar to the experimental device in~\cite{wu2015critical}. The
  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
  $45\mu$m. The fluid flux along the red regions is into the vesicle,
  and the fluid flux along the blue regions is out of the vesicle.
  (a--c): The ability for a semipermeable vesicle to pass through the
  contraction depends on the semipermeability rate. (d--f): The ability
  for a semipermeable vesicle to pass through the contraction depends
  on the flow rate. The colored vesicles show the tension distribution
  in N/m of the circled vesicles. Throughout the entire simulation,
  these vesicle configurations have the largest tension.}
\end{figure}

@@

\begin{figure*}[htp]
  \centering
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/contractingTensions1.pdf}
    };
    \node at (-8.62,4.3) {(a)};
    \node at (+1.1,4.3) {(c)};
    \node at (-8.62,-1.2) {(b)};
    \node at (+1.1,-1.2) {(d)};
  \end{tikzpicture}

  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=0.8\textwidth]{figures/contractingTensions2.pdf}
    };
    \node at (-6.79,1.4) {(e)};
  \end{tikzpicture}

  \caption{\label{fig:contractingTensions1} Tension distribution along a
  semi-permeable vesicle going through a contracting geometry. The
  vesicle tension increases by up to five orders of magnitude when as it
  enters the neck. The permeability constant and flow rates are (a)
  $U_{\max} = 5.7\mu$m/s, $\beta = 5 \times 10^{-4}$; (b) $U_{\max} =
  5.7\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} = 0.57\mu$m/s,
  $\beta = 1 \times 10^{-3}$; (d) $U_{\max} = 5.7\mu$m/s, $\beta = 1
  \times 10^{-3}$; (e) $U_{\max} = 18\mu$m/s, $\beta = 1 \times
  10^{-3}$.}
\end{figure*}

>>>>

\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} A contracting channel
  similar to the experimental configuration in~\cite{wu2015critical}. The
  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
  $45\mu$m. The fluid flux along the red regions is into the vesicle,
  and the fluid flux along the blue regions is out of the vesicle.
  (a--c): The ability for a semipermeable vesicle to pass through the
  contraction depends on the semipermeability rate. (d--f): The ability
  for a semipermeable vesicle to pass through the contraction depends
  on the flow rate. The colored vesicles show the tension distribution
  in N/m of the circled vesicles. Throughout the entire simulation,
  these vesicle configurations have the largest tension.}
\end{figure}

@@

\subsection*{Vesicle going through a contracting channel (slit)}
When a semipermeable vesicle goes through a contracting channel (slit) the numerical simulations show that both the driving flow and the membrane permeability have to be sufficiently large for a successful passage through the slit, see Figure \ref{fig:contractingComposite}.  As the vesicle goes through the contracting channel, the gradual confinement first leads to a slow inflation. Once the vesicle is close to the neck, it quickly deflates in order to fit the constriction. When the vesicle is near the neck, simulations show that the the water effluxes are in the front and rear of vesicle while most water influx is in the middle. The tension distribution along the vesicle as a function of their position in the contracting channel is summarized in Figure~\ref{fig:contractingTension1}, where we observe the membrane tension has the largest magnitude when the vesicle is at the neck. Away from the neck the membrane tension is quite small due to th
\begin{figure*}[htp]
  \centering
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/contractingTensions1.pdf}
    };
    \node at (-8.62,4.3) {(a)};
    \node at (+1.1,4.3) {(c)};
    \node at (-8.62,-1.2) {(b)};
    \node at (+1.1,-1.2) {(d)};
  \end{tikzpicture}
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=0.8\textwidth]{figures/contractingTensions2.pdf}
    };
    \node at (-6.79,1.4) {(e)};
  \end{tikzpicture}
  \caption{\label{fig:contractingTensions1} Tension distribution along a
  semi-permeable vesicle going through a contracting geometry. The
  vesicle tension increases by up to five orders of magnitude when as it
  enters the neck. The permeability constant and flow rates are (a)
  $U_{\max} = 5.7\mu$m/s, $\beta = 5 \times 10^{-4}$; (b) $U_{\max} =
  5.7\mu$m/s, $\beta = 5 \times 10^{-3}$; (c) $U_{\max} = 0.57\mu$m/s,
  $\beta = 1 \times 10^{-3}$; (d) $U_{\max} = 5.7\mu$m/s, $\beta = 1
  \times 10^{-3}$; (e) $U_{\max} = 18\mu$m/s, $\beta = 1 \times
  10^{-3}$.}
\end{figure*}
